% ============================================================================
% APPENDIX B: PAPER DATABASE
% ============================================================================

\chapter{Literature Database}
\label{app:papers}

This appendix provides a comprehensive database of papers reviewed in this literature review, organized by category and relevance tier.

% ============================================================================
% B.1: TIER 1 - ESSENTIAL PAPERS
% ============================================================================

\section{Tier 1: Essential Papers}
\label{app:tier1}

These papers are fundamental to understanding satellite-based QKD and directly relevant to Nguyen et al. (2021).

\begin{longtable}{p{0.5cm}p{3cm}p{5cm}p{2cm}p{2.5cm}}
\caption{Tier 1 Essential Papers} \\
\toprule
\textbf{\#} & \textbf{Authors} & \textbf{Title} & \textbf{Year} & \textbf{Journal} \\
\midrule
\endfirsthead
\multicolumn{5}{c}{\textit{Continued from previous page}} \\
\toprule
\textbf{\#} & \textbf{Authors} & \textbf{Title} & \textbf{Year} & \textbf{Journal} \\
\midrule
\endhead
\midrule
\multicolumn{5}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot

1 & Nguyen et al. & Reliability improvement of satellite-based QKD using retransmission & 2021 & Photonic Net. Comm. \\
2 & Chen et al. & Integrated space-to-ground quantum network over 4,600 km & 2021 & Nature \\
3 & Liao et al. & Satellite-to-ground quantum key distribution & 2017 & Nature \\
4 & Yin et al. & Satellite-based entanglement distribution over 1200 km & 2017 & Science \\
5 & Dequal et al. & Feasibility of satellite CV-QKD & 2021 & npj Quantum Info. \\
6 & Trinh et al. & DT/DD for QKD over FSO & 2018 & IEEE Access \\
7 & Pirandola et al. & Advances in quantum cryptography & 2020 & Adv. Opt. Photon. \\
8 & Nguyen et al. & CV-QKD with DT/HD scheme & 2023 & IEEE Access \\
\end{longtable}

% ============================================================================
% B.2: TIER 2 - IMPORTANT PAPERS
% ============================================================================

\section{Tier 2: Important Papers}
\label{app:tier2}

These papers provide essential context and technical foundations.

\begin{longtable}{p{0.5cm}p{3cm}p{5cm}p{2cm}p{2.5cm}}
\caption{Tier 2 Important Papers} \\
\toprule
\textbf{\#} & \textbf{Authors} & \textbf{Title} & \textbf{Year} & \textbf{Journal} \\
\midrule
\endfirsthead
\multicolumn{5}{c}{\textit{Continued from previous page}} \\
\toprule
\textbf{\#} & \textbf{Authors} & \textbf{Title} & \textbf{Year} & \textbf{Journal} \\
\midrule
\endhead
\midrule
\multicolumn{5}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot

9 & Scarani et al. & Security of practical QKD & 2009 & Rev. Mod. Phys. \\
10 & Xu et al. & Secure QKD with realistic devices & 2020 & Rev. Mod. Phys. \\
11 & Tomamichel et al. & Tight finite-key analysis & 2012 & Nature Comm. \\
12 & Vasylyev et al. & Atmospheric quantum channels & 2016 & Phys. Rev. A \\
13 & Liorni et al. & Satellite QKD beam and weather effects & 2019 & New J. Phys. \\
14 & Ma et al. & Satellite downlink Gamma-Gamma & 2015 & Appl. Opt. \\
15 & Orsucci et al. & Practical satellite QKD architectures & 2025 & Int. J. Sat. Comm. \\
16 & Mueller et al. & CASCADE and LDPC for QKD & 2025 & IET Quantum Comm. \\
17 & Liao et al. & Intercontinental quantum network & 2018 & Phys. Rev. Lett. \\
\end{longtable}

% ============================================================================
% B.3: TIER 3 - SUPPORTING PAPERS
% ============================================================================

\section{Tier 3: Supporting Papers}
\label{app:tier3}

These papers provide additional technical depth and context.

\begin{longtable}{p{0.5cm}p{3cm}p{5cm}p{2cm}p{2.5cm}}
\caption{Tier 3 Supporting Papers} \\
\toprule
\textbf{\#} & \textbf{Authors} & \textbf{Title} & \textbf{Year} & \textbf{Journal} \\
\midrule
\endfirsthead
\multicolumn{5}{c}{\textit{Continued from previous page}} \\
\toprule
\textbf{\#} & \textbf{Authors} & \textbf{Title} & \textbf{Year} & \textbf{Journal} \\
\midrule
\endhead
\midrule
\multicolumn{5}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot

18 & Al-Habash et al. & Gamma-Gamma distribution derivation & 2001 & Opt. Eng. \\
19 & Grosshans et al. & CV-QKD with coherent states & 2003 & Nature \\
20 & Leverrier & Composable security for CV-QKD & 2015 & Phys. Rev. Lett. \\
21 & Milicevic et al. & Quasi-cyclic LDPC for QKD & 2018 & npj Quantum Info. \\
22 & Kish et al. & CV-QKD satellite feasibility & 2020 & Quantum Eng. \\
23 & Various & LEO constellation networking & 2022 & Entropy \\
24 & Various & Greek LEO QKD infrastructure & 2021 & Photonics \\
\end{longtable}

% ============================================================================
% B.4: TIER 4 - REFERENCE PAPERS
% ============================================================================

\section{Tier 4: Reference Papers}
\label{app:tier4}

These foundational papers provide historical and theoretical context.

\begin{longtable}{p{0.5cm}p{3cm}p{5cm}p{2cm}p{2.5cm}}
\caption{Tier 4 Reference Papers} \\
\toprule
\textbf{\#} & \textbf{Authors} & \textbf{Title} & \textbf{Year} & \textbf{Journal} \\
\midrule
\endfirsthead
\multicolumn{5}{c}{\textit{Continued from previous page}} \\
\toprule
\textbf{\#} & \textbf{Authors} & \textbf{Title} & \textbf{Year} & \textbf{Journal} \\
\midrule
\endhead
\midrule
\multicolumn{5}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot

25 & Bennett \& Brassard & BB84 protocol & 1984 & IEEE Conf. \\
26 & Ekert & E91 protocol & 1991 & Phys. Rev. Lett. \\
27 & Gisin et al. & Quantum cryptography review & 2002 & Rev. Mod. Phys. \\
28 & Bedington et al. & Progress in satellite QKD & 2017 & npj Quantum Info. \\
29 & Kaushal \& Kaddoum & Space optical communication & 2017 & IEEE Comm. Surv. \\
30 & Pan et al. & Micius experiments review & 2022 & Rev. Mod. Phys. \\
\end{longtable}

% ============================================================================
% B.5: VIETNAMESE/PTIT PAPERS
% ============================================================================

\section{Vietnamese/PTIT Research Papers}
\label{app:vietnamese}

Papers from Vietnamese institutions, particularly PTIT.

\begin{longtable}{p{0.5cm}p{3cm}p{5cm}p{2cm}p{2.5cm}}
\caption{Vietnamese/PTIT Research Papers} \\
\toprule
\textbf{\#} & \textbf{Authors} & \textbf{Title} & \textbf{Year} & \textbf{Venue} \\
\midrule
\endfirsthead
\multicolumn{5}{c}{\textit{Continued from previous page}} \\
\toprule
\textbf{\#} & \textbf{Authors} & \textbf{Title} & \textbf{Year} & \textbf{Venue} \\
\midrule
\endhead
\midrule
\multicolumn{5}{r}{\textit{Continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot

V1 & Trinh et al. & DT/DD for QKD over FSO & 2018 & IEEE Access \\
V2 & Vu et al. & HAP-aided satellite QKD & 2019 & VTC Spring \\
V3 & Nguyen et al. & Reliability with retransmission & 2021 & Photonic Net. Comm. \\
V4 & Nguyen et al. & CV-QKD with DT/HD & 2023 & IEEE Access \\
V5 & Vu et al. & Network coding EB/PM QKD & 2023 & ITC-CSCC \\
\end{longtable}

% ============================================================================
% B.6: PAPERS BY CATEGORY
% ============================================================================

\section{Papers by Category}
\label{app:by_category}

\subsection{Foundational QKD Protocols}
\begin{itemize}
    \item Bennett \& Brassard (1984) - BB84
    \item Ekert (1991) - E91
    \item Grosshans et al. (2003) - CV-QKD
    \item Gisin et al. (2002) - Review
\end{itemize}

\subsection{Satellite QKD Experiments}
\begin{itemize}
    \item Liao et al. (2017) - Micius first QKD
    \item Yin et al. (2017) - Entanglement distribution
    \item Liao et al. (2018) - Intercontinental QKD
    \item Chen et al. (2021) - Integrated network
    \item Pan et al. (2022) - Micius review
\end{itemize}

\subsection{Atmospheric Channel Models}
\begin{itemize}
    \item Al-Habash et al. (2001) - Gamma-Gamma
    \item Vasylyev et al. (2016) - Quantum channels
    \item Liorni et al. (2019) - Weather effects
    \item Ma et al. (2015) - Satellite downlink
    \item Kaushal \& Kaddoum (2017) - Space optical
\end{itemize}

\subsection{Detection and Modulation}
\begin{itemize}
    \item Trinh et al. (2018) - DT/DD
    \item Nguyen et al. (2021) - DT/HD
    \item Nguyen et al. (2023) - CV-QKD DT/HD
    \item Dequal et al. (2021) - CV-QKD satellite
\end{itemize}

\subsection{Error Correction}
\begin{itemize}
    \item Milicevic et al. (2018) - LDPC
    \item Mueller et al. (2025) - CASCADE vs LDPC
    \item Various (2024) - RC-LDPC-Polar
\end{itemize}

\subsection{Security Analysis}
\begin{itemize}
    \item Scarani et al. (2009) - Practical security
    \item Tomamichel et al. (2012) - Finite-key
    \item Xu et al. (2020) - Realistic devices
    \item Leverrier (2015) - CV-QKD security
\end{itemize}

\subsection{Recent Advances (2022-2025)}
\begin{itemize}
    \item Orsucci et al. (2025) - Architecture assessment
    \item Mueller et al. (2025) - Industrial reconciliation
    \item Various (2025) - Finite-key heterodyne
    \item LEO constellation studies (2022-2024)
\end{itemize}

% ============================================================================
% B.7: CITATION STATISTICS
% ============================================================================

\section{Citation Statistics}
\label{app:citations}

\begin{table}[h]
\centering
\caption{High-Citation Papers in Review}
\label{tab:high_citations}
\begin{tabular}{lcc}
\toprule
\textbf{Paper} & \textbf{Est. Citations} & \textbf{Year} \\
\midrule
Bennett \& Brassard (BB84) & $>$15,000 & 1984 \\
Gisin et al. (Review) & $>$5,000 & 2002 \\
Ekert (E91) & $>$5,000 & 1991 \\
Scarani et al. (Security) & $>$4,000 & 2009 \\
Liao et al. (Micius) & $>$2,500 & 2017 \\
Yin et al. (Entanglement) & $>$2,000 & 2017 \\
Pirandola et al. (Review) & $>$1,500 & 2020 \\
Chen et al. (Network) & $>$1,000 & 2021 \\
Grosshans et al. (CV-QKD) & $>$1,000 & 2003 \\
Xu et al. (Devices) & $>$800 & 2020 \\
\bottomrule
\end{tabular}
\end{table}

% ============================================================================
% B.8: DOWNLOAD INFORMATION
% ============================================================================

\section{Paper Access Information}
\label{app:access}

\subsection{Open Access Sources}
\begin{itemize}
    \item \textbf{arXiv:} Most physics papers available (arxiv.org)
    \item \textbf{PubMed Central:} Some biomedical-related papers
    \item \textbf{IEEE Xplore:} Some open access articles
    \item \textbf{Nature/Science:} Selected open access papers
\end{itemize}

\subsection{Institutional Access}
\begin{itemize}
    \item USTH library portal
    \item VAST institutional subscriptions
    \item Inter-library loan services
\end{itemize}

\subsection{DOI References}
Key DOIs for direct access:
\begin{itemize}
    \item Nguyen et al. (2021): 10.1007/s11107-021-00934-y
    \item Chen et al. (2021): 10.1038/s41586-020-03093-8
    \item Liao et al. (2017): 10.1038/nature23655
    \item Pirandola et al. (2020): 10.1364/AOP.361502
    \item Trinh et al. (2018): 10.1109/ACCESS.2018.2796046
\end{itemize}
